Adaptive evolution with aneuploidy and mutation

### 2022-01-18 ms/ms.tex
..
fig 2 revised caption and added todos

% FIG posterior
\begin{figure}[h!]
  \centering
\includegraphics[width=0.9\textwidth]{../figures/posterior.pdf}
  \caption{
  \textbf{Posterior distribution of single-locus model.}
% TODO histogram on diagonal, 2d histogram without interpolation below diagonal
% TODO mutation rate tick labels should be in 10^-6, not 10^-5, and write 10^-6 not 1e-5; also it looks like you get positive density for mutation rate = 0 which doesnt make sense - set limit to 0.
% change trisomy rate to aneuploidy gain rate
% remove "mutation rate" from y label on top-left
% remove the y-ticks from the diagonal, they are meaningless, right?
% Fitness of 2n+1, w_{2n+1} (not 2n+1 fitness)
% TODO change dashed orange to red and make it a bit bolder.
On the diagonal, the posterior kernel density estimate for each parameter. 
Below the diagonal, joint posterior density of two parameters (dark purple and bright yellow for low and high density, respectively). Red markers and orange lines for the joint MAP estimates (which may differ from the marginal maximum density, as the marginal distribution integrates over all other parameters).
} 
  \label{fig:posterior}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

>>>>

% FIG posterior
\begin{figure}[h!]
  \centering
\includegraphics[width=0.9\textwidth]{../figures/posterior.pdf}
  \caption{
  \textbf{Posterior distribution of single-locus model.}
On the diagonal, the posterior kernel distribution of each model parameter. 
Below the diagonal, joint posterior distribution of pairs of model parameters (dark purple and bright yellow for low and high density, respectively). Red markers and orange lines for the joint MAP estimate (which may differ from the marginal MAP, as the marginal distribution integrates over all other parameters).
} 
% TODO less y axis ticks
% more x axes ticks?
  \label{fig:posterior}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%
